Continuous gravitational waves in the lab: recovering audio signals with a table-top optical microphone

### 2020-06-29 paper/ifo-complexAudio.tex
figures from Changrong and editing complex audio

Band-passing the signal similarly does not address the remaining harmonics above $100\,{\rm Hz}$. 
However, it does suppress other noise at higher frequencies. 
The best performing band-pass filter we find is a fifth order ($n = 5$) Butterworth filter over the range $150\,{\rm Hz}$--$3\,{\rm kHz}$ (beyond $2\,{\rm kHz}$ speech information content drops significantly~\cite{speech_intelligibility}). 
For a low-pass Butterworth filter with cut-off frequency $\omega_c$ and gain $\epsilon$, the frequency response (attenuation at each frequency) is,
\begin{equation}
\label{eq:butterworth}
H(\omega) = \frac{1}{\sqrt{1+\epsilon^2 (\omega/\omega_c)^{2n}}},
\end{equation}
as a function of frequency $\omega$. 
To construct a Butterworth band-pass filter, the low-pass filter in Eq.~\ref{eq:butterworth} is combined with a high-pass filter of similar form. 
The response of the filter used is shown in Figure~\ref{fig:butterworth}. 
The Butterworth filter performs the well as it is optimised to be `maximally flat' within the band region, prioritising the condition ii) .
This filter improves on the above simpler filters but recordings of speech still have low intelligibility.
They can be recognised as speech without being understood.
Looking forward to Sec.~\ref{sec:logmmse}, results for the Butterworth filter are shown in combination with a speech enhancement technique.

@@

The combination of the notch filter and the Wiener filter results are shown in the 
%The ideal filter would be one that i) completely attenuates the undesired parts of the spectrum, ii) does not change the rest of the spectrum, and iii) has smooth edges so as to not damage the signal after convolution. 
%These three conditions are contradictory and any filter must compromise between them. 
%The above simple filters fail one or more of i)--iii). 
%The Butterworth filter performs the best as it is optimised to be `maximally flat' within the band region, prioritising the second condition.
%\han{see note from Andrew and ask James about this}

>>>>

Band-passing the signal similarly does not address the remaining harmonics above $100\,{\rm Hz}$. 
However, it does suppress other noise at higher frequencies. 
The best performing band-pass filter we find is a fifth order ($n = 5$) Butterworth filter over the range $150\,{\rm Hz}$--$3\,{\rm kHz}$ (beyond $2\,{\rm kHz}$ speech information content drops significantly~\cite{speech_intelligibility}). 
For a low-pass Butterworth filter with cut-off frequency $\omega_c$ and gain $\epsilon$, the frequency response (attenuation at each frequency) is,
\begin{equation}
\label{eq:butterworth}
H(\omega) = \frac{1}{\sqrt{1+\epsilon^2 (\omega/\omega_c)^{2n}}},
\end{equation}
as a function of frequency $\omega$. 
To construct a Butterworth band-pass filter, the low-pass filter in Eq.~\ref{eq:butterworth} is combined with a high-pass filter of similar form. 
The response of the filter used is shown in Figure~\ref{fig:butterworth}. 
The Butterworth filter performs the well as it is optimised to be `maximally flat' within the band region (prioritising condition (ii) above).
This filter improves on the above simpler filters but recordings of speech still have low intelligibility.
They can be recognised as speech without being understood.
Looking forward to Sec.~\ref{sec:logmmse}, results for the Butterworth filter are shown in combination with a speech enhancement technique.

@@

The combination of the notch filter and the Wiener filter produces a cleaner signal than either individually. 
The time series and spectrum results are shown in the final panels of Figs.~\ref{fig:timeNotchWiener} and ~\ref{fig:freqNotchWiener} respectively.
\han{todo - ask Changrong for some concluding remarks on intelligibility of the result using notch and wiener filter}

%The ideal filter would be one that i) completely attenuates the undesired parts of the spectrum, ii) does not change the rest of the spectrum, and iii) has smooth edges so as to not damage the signal after convolution. 
%These three conditions are contradictory and any filter must compromise between them. 
%The above simple filters fail one or more of i)--iii). 
%The Butterworth filter performs the best as it is optimised to be `maximally flat' within the band region, prioritising the second condition.
%\han{see note from Andrew and ask James about this}
